
\documentclass[a4paper]{article}

\usepackage{fullpage} % Package to use full page
\usepackage{parskip} % Package to tweak paragraph skipping
\usepackage{tikz} % Package for drawing
\usepackage{amsmath}
\usepackage{hyperref}

\title{Economics 201 HW 2}
\author{Joshua Reed}
\date{\today}

\begin{document}

\maketitle

\section{My Firm's Product}

Before returning to school I worked as an intern at Mentor Graphics. The main product
sold by (my division) Mentor Graphics is Calibre Electronic Design Automation software.

\subsection{Number of firms} 
Major players including Synopsis, Cadence, and Mentor.

Total: 3

\subsection{Product uniformity} 
Mentor targets the most advanced node designs, and as such,
Mentor's products don't overlap much with their competitors. Each of the 'big three' tend 
to specialize in one are. Cadence is design, Mentor's is Pre-Silicon, and Synopsis is post
silicone.

\subsection{Ease of entry and exit} 
To enter and exit the EDA industry is at minimum a several 
million dollar endeavor. It is not at all easy to enter or exit from the EDA industry.

\subsection{Market type} 
At first brush, the EDA market looks oligopolistic; however, due to 
specialization, none of the software products are perfect substitutes for each other. 
Mentor Graphics operates in a monopolistic competition market structure.





\section{Cost of Living Increase}
Wage decrease causing more hours worked is primarily a substitution effect. The worker strives
to keep the same income by substituting leisure time for work.

\newpage

\section{Game Theory Matrix}

\subsection{Matrix}

\vspace{8cm}

\subsection{Outcome} 
Testifying to having cheated is the dominant strategy for both parties, and the 
dominant strategy equilibrium is both signing and receiving an F in the course. Therefore
this it is the most likely outcome.

\section{Labor Supply Curve}

\subsection{Plot}

\vspace{8cm}

\subsection{Type of Graph} 
The curve is known as the backward-bending supply curve of labor.
At a certain point, substitution and income effects meet and switch.
\end{document}






